Experience Report: Haskell in Computational Biology

### 2012-03-11 mrfy_experience_report.tex
some love for verbs

A~little knowledge of and a lot of love for functional programming was
enough for us to carry out a successful research project in a language
that is rarely used in computational biology.
If~you \emph{want} to use Haskell---or one of your graduate students
wants to use Haskell---you can
succeed.

>>>>

A~little knowledge of and a lot of love for functional programming was
enough for us to carry out a successful research project in a language
that computational biologists seldom use.
If~you \emph{want} to use Haskell---or one of your graduate students
wants to use Haskell---you can
succeed.
